---
title: "Covid_data_analysis"
author: "Yongqi Liang"
date: "22/03/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(lubridate)
library(forecast)
library(tseries)
options(scipen = 999)
```

read files:
```{r}
cases_daily <- read_csv("time_series_covid19_confirmed_global.csv")
pop <- read_csv("UID_ISO_FIPS_LookUp_Table.csv")
head(pop)
```


task1: the world cases time series:
```{r}
cum_world <- cases_daily %>% 
  select(c(-1, -2, -3, -4)) %>%
  summarise_all(sum) %>% 
  slice(1) %>%
  unlist(., use.names=FALSE)

world <- diff(c(0, cum_world))

min(world)

time<-seq(as.Date("2020/1/22"),length.out=14,by="2 months")
```

plot:
```{r, fig.height=10, fig.width=20}
`Number of Daily New Cases` <- ts(world, frequency=365, start=2020)
plot.ts(`Number of Daily New Cases`,axes=F)
axis(2) # plot the y axis
axis(1, labels=time, at=seq(from=2020, by=0.17, length.out=length(time)))
box() # and the box around the plot
```


task2: find the top 5 countries which have the most total cases
```{r}
new_cases_by_country <- cases_daily %>%
  select(c(-1, -3, -4)) %>%
  group_by(`Country/Region`) %>%
  summarise(across(where(is.numeric), ~ sum(.x, na.rm = TRUE)))

new_cases_by_country %>% 
  rowwise(`Country/Region`) %>% 
  summarise(total_cases = sum(c_across(`1/22/20`:`3/20/22`)))
```

```{r}
total_cases_by_country <- cases_daily %>%
  select(c(-1, -3, -4)) %>%
  group_by(`Country/Region`) %>%
  summarise(cum = sum(`3/20/22`, na.rm = TRUE)) %>%
  arrange(desc(cum))

top5cases_country <- total_cases_by_country[1:5, ] %>% mutate(`Country/Region` = factor(`Country/Region`,levels=c("United Kingdom", "France","Brazil", "India", "US")))

#plot
top5cases_country %>% ggplot(aes(x = `Country/Region`, y = cum)) + geom_bar(stat="identity", fill = "#FF6666") + ylab("Cumulative confirmed cases") + labs(title = "Top 5 Country/Region by Cumulative confirmed cases") + theme(plot.title = element_text(hjust = 0.5)) + coord_flip()
```

task3: top 5 countries which has the largest percentage of cases
```{r}
clean_pop <- pop %>% group_by(Country_Region) %>%
  filter(is.na(Province_State)) %>% #merge population of the regions within the same country
  filter(Population>0) %>%
  select(c(8, 12))
 

#join table:
country_per <- total_cases_by_country %>%
  inner_join(clean_pop, by=c(`Country/Region`="Country_Region")) %>%
  mutate(percentage = cum/Population) %>%
  arrange(desc(percentage))

# find the population of top 5 from task2
country_per %>% filter(`Country/Region` %in% c("United Kingdom", "France","Brazil", "India", "US")) %>%
  mutate(diff = Population-cum)

```

task4: predict
(1)plot
```{r, fig.height=6, fig.width=10}
data <- ts(world, frequency=365, start=2020)
# Number of Daily New Cases for 2020/1/22-2022/3/20 plotted as time series
par(las=3)
plot(data, xlab="", ylab = "Number of Daily New Cases", xaxt="n",col="red")
axis(2) # plot the y axis
axis(1, labels=time, at=seq(from=2020, by=0.17, length.out=length(time)))
box()
```

Differenced: 
```{r}
# Differenced data to make stationery on mean
plot(diff(data),ylab="Differenced Number of Daily New Cases", xaxt="n",xlab="",col="red")
axis(2) # plot the y axis
axis(1, labels=time, at=seq(from=2020, by=0.17, length.out=length(time)))
```




log: 
```{r}
# log transform data to make stationery on variance
plot(log10(data),ylab="Log10(Number of Daily New Cases)", xaxt="n",xlab="",col="red")
axis(2) # plot the y axis
axis(1, labels=time, at=seq(from=2020, by=0.17, length.out=length(time)))
```


diff+log: 
```{r}
# differenced log transform data to make data stationery on both mean and variance
plot(diff(log10(data)),xlab="",ylab="Differenced Log (Number of Daily New Cases)", xaxt="n",col="red")
axis(2) # plot the y axis
axis(1, labels=time, at=seq(from=2020, by=0.168, length.out=length(time)))
par(mfrow = c(1,2))
```

Augmented Dickey-Fuller Test:
```{r}
adf.test(data)
adf.test(diff(data))
adf.test(log10(data))
adf.test(diff(log10(data))) # selected
```


(2)
test acf and pacf

using data
```{r}
acf(ts(data),main="ACF Number of Daily New Cases",col="green")
pacf(ts(data),main="PACF Number of Daily New Cases", col="green")
```


using diff(log10(data))) ---- stationary data
```{r}
acf(ts(diff(log10(data))),main="ACF Number of Daily New Cases",col="green")
pacf(ts(diff(log10(data))),main="PACF Number of Daily New Cases", col="green")
```



(3)
```{r}
require(forecast)
AR <- auto.arima((log10(data)), approximation=FALSE,trace=FALSE)
summary(AR)
par(bg = "white")
pred <- predict(AR, n.ahead = 30)
pred
pred$pred
plot(data,col="red",xaxt="n" ,xlab = "",ylab = "Number of Daily New Cases",main="Number of Daily New Cases Forecast for the next 30 days")
lines(10^(pred$pred),col="blue" ,xaxt="n")
#lines(10^(pred$pred+2*pred$se),col="green")
#lines(10^(pred$pred-2*pred$se),col="green")

par(las=3)

time2<-seq(as.Date("2020/1/22"),length.out=10,by="3 months")  
axis(1, labels=time2, at=seq(from=2020, by=0.2493, length.out=length(time2)))
```

```{r}
acf(ts(AR$residuals),main='ACF Residual')
pacf(ts(AR$residuals),main='PACF Residual')
```

```{r}
#Only the Predicted Plot
plot(10^(pred$pred),col="blue", xaxt = "n", xlab="",ylab="Number of Daily New Cases",main="Number of Daily New Cases Forecast for the next 30 days")
time3<-seq(as.Date("2022/3/21"),length.out=11,by="3 days") 
axis(1, labels=time3, at=seq(from=2022.16, by=0.0081, length.out=length(time3)), cex.axis=0.6)
```


US data
```{r}
US_cum <- new_cases_by_country %>% 
  filter(`Country/Region` == "US") %>%
  select(-1) %>%
  slice(1) %>%
  unlist(., use.names=FALSE)


US <- diff(c(0, US_cum))[39:789]

for (n in seq(1, length(US), 1)) {
  if (US[n] >910000) US[n] = mean(US[n-1], US[n+1])
}

US_data <- ts(US, frequency=365, start=2020)
# Number of Daily New Cases for 2020/1/22-2022/3/20 plotted as time series
par(las=3)
plot(US_data, xlab="", ylab = "Number of Daily New Cases", xaxt="n",col="red")
axis(2) # plot the y axis
axis(1, labels=time, at=seq(from=2020, by=0.159, length.out=length(time)))
box()
```


```{r}
acf(ts(US_data),main="ACF Number of Daily New Cases",col="green")
pacf(ts(US_data),main="PACF Number of Daily New Cases", col="green")
```

adf test
```{r}
adf.test(diff(log10(US_data)))
```

```{r}
plot(diff(log10(US_data)),xlab="",ylab="Differenced Log (Number of Daily New Cases)", xaxt="n",col="red")
axis(2) # plot the y axis
axis(1, labels=time, at=seq(from=2020, by=0.156, length.out=length(time)))
```


using diff(log10(data))) ---- stationary data
```{r}
acf(ts(diff(log10(US_data))),main="ACF Number of Daily New Cases",col="green")
pacf(ts(diff(log10(US_data))),main="PACF Number of Daily New Cases", col="green")
```


```{r}
US_AR <- auto.arima((log10(US_data)), approximation=FALSE,trace=FALSE)
summary(US_AR)
par(bg = "white")
US_pred <- predict(US_AR, n.ahead = 30)
US_pred
10^US_pred$pred
plot(US_data,col="red",xaxt="n" ,xlab = "",ylab = "Number of Daily New Cases",main="Number of Daily New Cases Forecast for the next 30 days in the US")
lines(10^(US_pred$pred),col="blue" ,xaxt="n")
#lines(10^(US_pred$pred+2*US_pred$se),col="green")
#lines(10^(US_pred$pred-2*US_pred$se),col="green")

par(las=3)

time2<-seq(as.Date("2020/1/22"),length.out=10,by="3 months")  
axis(1, labels=time2, at=seq(from=2020, by=0.2493, length.out=length(time2)))

```

```{r}
#Only the Predicted Plot
plot(10^(US_pred$pred),col="blue", xaxt = "n", xlab="",ylab="Number of Daily New Cases",main="Number of Daily New Cases Forecast for the next 30 days in the US")
time3<-seq(as.Date("2022/3/21"),length.out=11,by="3 days") 
axis(1, labels=time3, at=seq(from=2022.06, by=0.0081, length.out=length(time3)), cex.axis=0.6)
```
```{r}
acf(ts(US_AR$residuals),main='ACF Residual')
pacf(ts(US_AR$residuals),main='PACF Residual')
```









india:
```{r}
id_cum <- new_cases_by_country %>% 
  filter(`Country/Region` == "India") %>%
  select(-1) %>%
  slice(1) %>%
  unlist(., use.names=FALSE)


id <- diff(c(0, id_cum))[43:789]

for (n in seq(1, length(id), 1)) {
  if (id[n] == 0) id[n] = mean(id[n-1], id[n+1])
}

id_data <- ts(id, frequency=365, start=2020)
# Number of Daily New Cases for 2020/1/22-2022/3/20 plotted as time series
par(las=3)
plot(id_data, xlab="", ylab = "Number of Daily New Cases", xaxt="n",col="red")
axis(2) # plot the y axis
axis(1, labels=time, at=seq(from=2020, by=0.17, length.out=length(time)))
box()
```

```{r}
acf(ts(id_data),main="ACF Number of Daily New Cases",col="green")
pacf(ts(id_data),main="PACF Number of Daily New Cases", col="green")
```

using diff(log10(data))) ---- stationary data
```{r}
acf(ts(diff(log10(id_data))),main="ACF Number of Daily New Cases",col="green")
pacf(ts(diff(log10(id_data))),main="PACF Number of Daily New Cases", col="green")
```

adf test
```{r}
adf.test(diff(log10(id_data)))
```


```{r}
id_AR <- auto.arima((log10(id_data)), approximation=FALSE,trace=FALSE)
summary(id_AR)
par(bg = "white")
id_pred <- predict(id_AR, n.ahead = 30)
id_pred
10^id_pred$pred
plot(id_data,col="red",xaxt="n" ,xlab = "",ylab = "Number of Daily New Cases",main="Number of Daily New Cases Forecast for the next 30 days")
lines(10^(id_pred$pred),col="blue" ,xaxt="n")
#lines(10^(US_pred$pred+2*US_pred$se),col="green")
#lines(10^(US_pred$pred-2*US_pred$se),col="green")

par(las=3)

time2<-seq(as.Date("2020/1/22"),length.out=10,by="3 months")  
axis(1, labels=time2, at=seq(from=2020, by=0.2493, length.out=length(time2)))

```

```{r}
#Only the Predicted Plot
plot(10^(id_pred$pred),col="blue", xaxt = "n", xlab="",ylab="Number of Daily New Cases",main="Number of Daily New Cases Forecast for the next 30 days")
time3<-seq(as.Date("2022/3/21"),length.out=11,by="3 days") 
axis(1, labels=time3, at=seq(from=2022.16, by=0.0081, length.out=length(time3)), cex.axis=0.6)
```


US omi data
```{r}
US_omi <- diff(c(0, US_cum))[650:789]
for (n in seq(1, length(US_omi), 1)) {
  if (US_omi[n] >910000) US_omi[n] = mean(US_omi[n-1], US_omi[n+1])
}

time_omi <- seq(as.Date("2021/11/20"),length.out=5,by="1 months") 

US_omi_data <- ts(US_omi, frequency=365, start=2021)
# Number of Daily New Cases for 2020/1/22-2022/3/20 plotted as time series
par(las=3)
plot(US_omi_data, xlab="", ylab = "Number of Daily New Cases in the US", xaxt="n",col="red")
axis(2) # plot the y axis
axis(1, labels=time_omi, at=seq(from=2021, by=0.095, length.out=length(time_omi)))
box()
```


data transforming:
```{r}
plot(diff(log10(US_omi_data)),xlab="",ylab="Differenced Log (Number of Daily New Cases)", xaxt="n",col="red")
axis(2) # plot the y axis
axis(1, labels=time_omi, at=seq(from=2021, by=0.095, length.out=length(time_omi)))
```

```{r}
acf(ts(US_omi_data),main="ACF Number of Daily New Cases",col="green")
pacf(ts(US_omi_data),main="PACF Number of Daily New Cases", col="green")
```


adf test
```{r}
adf.test(diff(log10(US_omi_data)))
```

using diff(log10(data)) ---- stationary data
```{r}
acf(ts(diff(log10(US_omi_data))),main="ACF Number of Daily New Cases",col="green")
pacf(ts(diff(log10(US_omi_data))),main="PACF Number of Daily New Cases", col="green")
```


```{r}
US_omi_AR <- auto.arima((log10(US_omi_data)), approximation=FALSE,trace=FALSE)
summary(US_omi_AR)
par(bg = "white")
US_omi_pred <- predict(US_omi_AR, n.ahead = 30)
US_omi_pred
US_omi_pred$pred
plot(US_omi_data ,xlim=c(2021.0,2021.5) ,xaxt="n", col="red" ,xlab = "",ylab = "Number of Daily New Cases",main="Number of Daily New Cases Forecast for the next 30 days in the US")
lines(10^(US_omi_pred$pred),col="blue", xaxt="n")
#lines(US_omi_pred$pred+2*US_omi_pred$se,col="green")
#lines(US_omi_pred$pred-2*US_omi_pred$se,col="green")

par(las=3)

time2_omi<-seq(as.Date("2021/11/20"),length.out=7,by="1 months")  
axis(1, labels=time2_omi, at=seq(from=2021, by=0.095, length.out=length(time2_omi)))

forecast(US_omi_AR, h = 30)
```

```{r}
#Only the Predicted Plot
plot(10^(US_omi_pred$pred), xaxt = "n", col="blue", xlab="",ylab="Number of Daily New Cases",main="Number of Daily New Cases Forecast for the next 30 days in the US")
time3<-seq(as.Date("2022/3/21"),length.out=11,by="3 days") 
axis(1, labels=time3, at=seq(from=2021.383, by=0.0081, length.out=length(time3)), cex.axis=0.6)
```


```{r}
acf(ts(US_omi_AR$residuals),main='ACF Residual')
pacf(ts(US_omi_AR$residuals),main='PACF Residual')
```






## nz omi data
```{r}
NZ_cum <- new_cases_by_country %>% 
  filter(`Country/Region` == "New Zealand") %>%
  select(-1) %>%
  slice(1) %>%
  unlist(., use.names=FALSE)


NZ_omi <- diff(c(0, NZ_cum))[650:789]

for (n in seq(1, length(NZ_omi)-1, 1)) {
  if (NZ_omi[n] == 0 | NZ_omi[n] > 25000) NZ_omi[n] = mean(NZ_omi[n-1], NZ_omi[n+1])
  if (NZ_omi[n+1]/NZ_omi[n] > 5) NZ_omi[n] = mean(NZ_omi[n-1], NZ_omi[n+1])
}


time_omi <- seq(as.Date("2021/11/20"),length.out=5,by="1 months") 

NZ_omi_data <- ts(NZ_omi, frequency=365, start=2021)
# Number of Daily New Cases for 2020/1/22-2022/3/20 plotted as time series
par(las=3)
plot(NZ_omi_data, xlab="", ylab = "Number of Daily New Cases in New Zealand", xaxt="n",col="red")
axis(2) # plot the y axis
axis(1, labels=time_omi, at=seq(from=2021, by=0.095, length.out=length(time_omi)))
box()
```
data transforming:
```{r}
plot(diff(log10(NZ_omi_data)),xlab="",ylab="Differenced Log (Number of Daily New Cases)", xaxt="n",col="red")
axis(2) # plot the y axis
axis(1, labels=time_omi, at=seq(from=2021, by=0.095, length.out=length(time_omi)))
```

```{r}
acf(ts(NZ_omi_data),main="ACF Number of Daily New Cases",col="green")
pacf(ts(NZ_omi_data),main="PACF Number of Daily New Cases", col="green")
```


adf test
```{r}
adf.test(diff(log10(NZ_omi_data)))
```

using diff(log10(data)) ---- stationary data
```{r}
acf(ts(diff(log10(NZ_omi_data))),main="ACF Number of Daily New Cases",col="green")
pacf(ts(diff(log10(NZ_omi_data))),main="PACF Number of Daily New Cases", col="green")
```


```{r}
NZ_omi_AR <- auto.arima((log10(NZ_omi_data)), approximation=FALSE,trace=FALSE)
summary(NZ_omi_AR)
par(bg = "white")
NZ_omi_pred <- predict(NZ_omi_AR, n.ahead = 30)
NZ_omi_pred
NZ_omi_pred$pred
plot(NZ_omi_data,xlim=c(2021.0,2021.5), col="red",xaxt="n" ,xlab = "",ylab = "Number of Daily New Cases",main="Number of Daily New Cases Forecast for the next 30 days in New Zealand")
lines(10^(NZ_omi_pred$pred),col="blue" ,xaxt="n")
#lines(US_omi_pred$pred+2*US_omi_pred$se,col="green")
#lines(US_omi_pred$pred-2*US_omi_pred$se,col="green")

par(las=3)

time2_omi<-seq(as.Date("2021/11/20"),length.out=7,by="1 months")  
axis(1, labels=time2_omi, at=seq(from=2021, by=0.095, length.out=length(time2_omi)))

forecast(NZ_omi_data, h = 30)
```

```{r}
#Only the Predicted Plot
plot(10^(NZ_omi_pred$pred),col="blue", xaxt = "n", xlab="",ylab="Number of Daily New Cases",main="Number of Daily New Cases Forecast for the next 30 days in New Zealand")
time3<-seq(as.Date("2022/3/21"),length.out=11,by="3 days") 
axis(1, labels=time3, at=seq(from=2021.383, by=0.0081, length.out=length(time3)), cex.axis=0.6)
```


```{r}
acf(ts(NZ_omi_AR$residuals),main='ACF Residual')
pacf(ts(NZ_omi_AR$residuals),main='PACF Residual')
```


## india OMI DATA:
```{r}
id_cum <- new_cases_by_country %>% 
  filter(`Country/Region` == "India") %>%
  select(-1) %>%
  slice(1) %>%
  unlist(., use.names=FALSE)


id_omi <- diff(c(0, id_cum))[650:789]

for (n in seq(1, length(id_omi), 1)) {
  if (id_omi[n] == 0) id_omi[n] = mean(id_omi[n-1], id_omi[n+1])
}

id_omi_data <- ts(id_omi, frequency=365, start=2021)
# Number of Daily New Cases for 2020/1/22-2022/3/20 plotted as time series
par(las=3)
plot(id_omi_data, xlab="", ylab = "Number of Daily New Cases", xaxt="n",col="red")
axis(2) # plot the y axis
axis(1, labels=time_omi, at=seq(from=2021, by=0.095, length.out=length(time_omi)))
box()
```
data transforming:
```{r}
plot(diff(log10(id_omi_data)),xlab="",ylab="Differenced Log (Number of Daily New Cases)", xaxt="n",col="red")
axis(2) # plot the y axis
axis(1, labels=time_omi, at=seq(from=2021, by=0.095, length.out=length(time_omi)))
```



```{r}
acf(ts(id_omi_data),main="ACF Number of Daily New Cases",col="green")
pacf(ts(id_omi_data),main="PACF Number of Daily New Cases", col="green")
```

using diff(log10(data))) ---- stationary data
```{r}
acf(ts(diff(log10(id_omi_data))),main="ACF Number of Daily New Cases",col="green")
pacf(ts(diff(log10(id_omi_data))),main="PACF Number of Daily New Cases", col="green")
```

adf test
```{r}
adf.test(diff(log10(id_omi_data)))
```


```{r}
id_omi_AR <- auto.arima((log10(id_omi_data)), approximation=FALSE,trace=FALSE)
summary(id_omi_AR)
par(bg = "white")
id_omi_pred <- predict(id_omi_AR, n.ahead = 30)
id_omi_pred
10^id_omi_pred$pred
plot(id_omi_data,xlim=c(2021.0,2021.5), col="red",xaxt="n" ,xlab = "",ylab = "Number of Daily New Cases",main="Number of Daily New Cases Forecast for the next 30 days in India")
lines(10^(id_omi_pred$pred),col="blue" ,xaxt="n")
#lines(10^(US_pred$pred+2*US_pred$se),col="green")
#lines(10^(US_pred$pred-2*US_pred$se),col="green")

par(las=3)
  
axis(1, labels=time2_omi, at=seq(from=2021, by=0.095, length.out=length(time2_omi)))

```

```{r}
#Only the Predicted Plot
plot(10^(id_omi_pred$pred),col="blue", xaxt = "n", xlab="",ylab="Number of Daily New Cases",main="Number of Daily New Cases Forecast for the next 30 days in India")
axis(1, labels=time3, at=seq(from=2021.383, by=0.0081, length.out=length(time3)), cex.axis=0.6)
```


## Brazil OMI DATA:
```{r}
br_cum <- new_cases_by_country %>% 
  filter(`Country/Region` == "Brazil") %>%
  select(-1) %>%
  slice(1) %>%
  unlist(., use.names=FALSE)


br_omi <- diff(c(0, br_cum))[650:789]

for (n in seq(1, length(br_omi)-1, 1)) {
  if (br_omi[n] == 0|br_omi[n]>300000) br_omi[n] = mean(br_omi[n-1], br_omi[n+1])
  if (br_omi[n+1]/br_omi[n] > 5) br_omi[n] = mean(br_omi[n-1], br_omi[n+1])
}

br_omi_data <- ts(br_omi, frequency=365, start=2021)
# Number of Daily New Cases for 2020/1/22-2022/3/20 plotted as time series
par(las=3)
plot(br_omi_data, xlab="", ylab = "Number of Daily New Cases", xaxt="n",col="red")
axis(2) # plot the y axis
axis(1, labels=time_omi, at=seq(from=2021, by=0.095, length.out=length(time_omi)))
box()
```
data transforming:
```{r}
plot(diff(log10(br_omi_data)),xlab="",ylab="Differenced Log (Number of Daily New Cases)", xaxt="n",col="red")
axis(2) # plot the y axis
axis(1, labels=time_omi, at=seq(from=2021, by=0.095, length.out=length(time_omi)))
```



```{r}
acf(ts(br_omi_data),main="ACF Number of Daily New Cases",col="green")
pacf(ts(br_omi_data),main="PACF Number of Daily New Cases", col="green")
```

using diff(log10(data))) ---- stationary data
```{r}
acf(ts(diff(log10(br_omi_data))),main="ACF Number of Daily New Cases",col="green")
pacf(ts(diff(log10(br_omi_data))),main="PACF Number of Daily New Cases", col="green")
```

adf test
```{r}
adf.test(diff(log10(br_omi_data)))
```


```{r}
br_omi_AR <- auto.arima(log10(br_omi_data))
summary(br_omi_AR)
par(bg = "white")
br_omi_pred <- predict(br_omi_AR, n.ahead = 30)
br_omi_pred
10^br_omi_pred$pred
plot(br_omi_data,xlim=c(2021.0,2021.5), col="red",xaxt="n" ,xlab = "",ylab = "Number of Daily New Cases",main="Number of Daily New Cases Forecast for the next 30 days in France")
lines(10^(br_omi_pred$pred),col="blue" ,xaxt="n")
#lines(10^(US_pred$pred+2*US_pred$se),col="green")
#lines(10^(US_pred$pred-2*US_pred$se),col="green")

par(las=3)
  
axis(1, labels=time2_omi, at=seq(from=2021, by=0.095, length.out=length(time2_omi)))

```

```{r}
#Only the Predicted Plot
plot(10^(br_omi_pred$pred),col="blue", xaxt = "n", xlab="",ylab="Number of Daily New Cases",main="Number of Daily New Cases Forecast for the next 30 days in France")
axis(1, labels=time3, at=seq(from=2021.383, by=0.0081, length.out=length(time3)), cex.axis=0.6)
```
## United Kingdom OMI DATA:
```{r}
uk_cum <- new_cases_by_country %>% 
  filter(`Country/Region` == "United Kingdom") %>%
  select(-1) %>%
  slice(1) %>%
  unlist(., use.names=FALSE)


uk_omi <- diff(c(0, uk_cum))[650:789]
uk_omi[139] = 74711
uk_omi[140] = 66733
uk_omi[102] = mean(67980,58860)

for (n in seq(1, length(uk_omi)-1, 1)) {
  if (uk_omi[n] == 0|uk_omi[n]>300000) uk_omi[n] = mean(uk_omi[n-1], uk_omi[n+1])
}

uk_omi_data <- ts(uk_omi, frequency=365, start=2021)
# Number of Daily New Cases for 2020/1/22-2022/3/20 plotted as time series
par(las=3)
plot(uk_omi_data, xlab="", ylab = "Number of Daily New Cases", xaxt="n",col="red")
axis(2) # plot the y axis
axis(1, labels=time_omi, at=seq(from=2021, by=0.095, length.out=length(time_omi)))
box()
```

```{r}

uk_omi_AR <- auto.arima(log10(uk_omi_data))
summary(uk_omi_AR)
par(bg = "white")
uk_omi_pred <- predict(uk_omi_AR, n.ahead = 30)
uk_omi_pred
10^uk_omi_pred$pred
plot(uk_omi_data,xlim=c(2021.0,2021.5), col="red",xaxt="n" ,xlab = "",ylab = "Number of Daily New Cases",main="Number of Daily New Cases Forecast for the next 30 days in UK")
lines(10^(uk_omi_pred$pred),col="blue" ,xaxt="n")
#lines(10^(US_pred$pred+2*US_pred$se),col="green")
#lines(10^(US_pred$pred-2*US_pred$se),col="green")

par(las=3)
  
axis(1, labels=time2_omi, at=seq(from=2021, by=0.095, length.out=length(time2_omi)))
#Only the Predicted Plot
plot(10^(uk_omi_pred$pred),col="blue", xaxt = "n", xlab="",ylab="Number of Daily New Cases",main="Number of Daily New Cases Forecast for the next 30 days in UK")
axis(1, labels=time3, at=seq(from=2021.383, by=0.0081, length.out=length(time3)), cex.axis=0.6)
```


